???A quantitative framework for investigating the reliability of network construction

### 2017-11-16 manuscript/CI_interactions.tex
Kate's edits to the manuscript. Comments enclosed in square brackets

    Efforts to account for variance in interaction frequencies are complicated by the fact that not only interaction frequencies but network structure vary over space and time. Community composition and species abundances vary from site to site~\citep{Baiser2012} and over time within a site~\citep{Olesen2011a}. The removal of a species from a site will obviously also remove its interactions. Interactions can also be lost, however, if participating species remain present but do not co-occur temporally or are too rare to detect each other~\citep{Tylianakis2010}, or through changes to individual preferences~\citep{Fodrie2015}.

    Beyond "true" variation in network structure, several researchers have pointed to the importance of sampling intensity for the assessment of network structure (e.g.,~\citealp{Martinez1999,Bluthgen2006,XX}). Despite this, the acknowledgement that insufficient sampling effort limits our ability to describe variation in ecological networks has not yet led to a quantitative framework to deal with the uncertainty generated by spatiotemporal variation in ecological interactions and by sampling.

@@

  To define the problem associated with describing ecological interaction networks, we will start from the perspective of an empirical community ecologist faced with the task of describing an interaction networks. This ecologist will be interested in generating a description of the blocks present, and the links between them (Roslin and Majaneva 2017). In other words, he or she seeks to fill in a matrix of species by species interactions. Importantly, the information sought is as much in the presence of given links as in the absence of others. An observed link will always remain an observed link, but to why given links are not observed, there may be multiple contributions. Thus, we will set off by contemplating what factors may contribute to links missing from the matrix. We consider that there are three nested levels of uncertainty making the occurrence of any interaction a stochastic process:

@@

    First, and most fundamentally, we do not know whether or not a pair of species have the appropriate characteristics to interact. We define the probability of an interaction $L$ as $P(L)=\lambda$. Obviously, because $k=0$, it is very likely that they cannot interact even if there were no time or environmental constraints preventing the interaction. But it is nonetheless possible that the interaction is a rare phenomenon that has never been documented before. This source of uncertainty is the one documented by trait-matching models~\citep{}. It arises because every model is imperfect and lacks information (i.e. traits) about the constraints on the interaction. In other words, with sufficient sampling and all information accessible, this interaction probability should either tend to 0 or to 1 and the uncertainty vanishes.

@@

    It could be that the interaction is feasible, i.e. $L=1$, but that it does not occur at a given location or moment in time because there are local constraints preventing it from occurring. We define the realisation of the interaction process $X$ given that the interaction is feasible as a stochastic process with associated probability $P(X|L)=\chi$. This phenomenon of interaction contingencies is usually not considered in network studies, but there is a rich literature in community ecology about the contingencies of interactions~\citep{}. 
    % We imagine for instance that an interaction between a gall and a parasitoid might not be recorded at a location because it was the wrong time of the year and the gall had not yet formed (phenological constraints), a late frost killed the larvae (an abiotic environmental constraint), another parasitoid species competitively excluded the parasitoid species of interest (a biotic environmental constraint) or simply the parasitoid is too rare to interact with all of its viable hosts (an abundance constraint).

@@

    Lastly, measurement errors are always source of uncertainty in the observation of ecological processes. We define the detection of an interaction $D$, given an interaction is feasible and occurs in the local conditions, as a stochastic process with associated probability $P(D|X,L)=\delta$. Detection failure could happen for several reasons, for instance if the rearing of a parasitoid fails with inappropriate lab conditions or because of species mis-identification. Some sources of detection error could be minimised with appropriate sampling effort ($\delta$ will converge to one with increasing number of collected galls), but other sources are often difficult to reduce (e.g. the occurrence of cryptic species might require molecular analysis for appropriate taxonomic identification).

@@

    The combination of these three sources of uncertainty together leads to many potential explanations for the observation of an absence of interaction, but only the situation where $L = 0$ (a true absence) is relevant for the investigation of networks. While the observation of an interaction is straightforward to interpret, absence of interactions must be decomposed in different quantities. It is particularly important to rule out the situations where $D=0 \cup X = 1 \cup L=1$, i.e. the interaction occurred at the location but was not observed, and $D=1 \cup X = 0 \cup L =1$, the interaction is feasible and would have been detected but did not occur at the local site.

  It is important to keep in mind that for network analysis, ecologists seek to measure the occurrence of true absences, which is the joint event $L=0 \cup X=1 \cup D=1$), but in reality they measure the marginal probability $P(L) = k/n$. % I'm pretty sure this should be L=0 but X=1 and D=1: interaction not feasible but site and detection perfect.

@@

  For the ecologist working on collecting network data, and on later interpreting these data, the considerations above raise a major challenge: how may we infer whether unobserved interactions went undetected due to sampling, or whether they truly do not occur. How then may we refine our sampling approaches to reduce uncertainties, and to gain insights into the impact of multiple processes on field observations? Importantly, some sources can be minimised with appropriate sampling design and efforts, while other sources are difficult or impossible to reduce – since they are generated by chance variation created by the very process in which we are interested.

  The basic information that we are collecting consists of matrices of interaction partners. Our count of interactions between species A and species B reflects uncertainty with respect to whether two species interact when co-occurring at a given site, chance variation in whether the interaction is realised, and uncertainty with respect to whether it is detected when realised. In this case, what can we do to pin down any of these different types of variation?

  A simple example will illustrate the problem: assume that we want to infer the probability of an interaction between two species, A and B. Now assume that in reality, interaction between A and B is completely impossible (i.e. the true $\lambda$= 0). Given no added detection error in observing the incidence of the interaction, then a single observation of species co-occurrence will reveal (very) little regarding the probability of the interaction – the confidence limits for one observation essentially spans from 0 to 1 (Fig.~\ref{upper_limits}). For 5 observations, this confidence limit will still extends to 0.5. Only with thirty observations will it shrink to 0.1. Thus, adding (many) more observations is certainly useful in controlling uncertainty due to stochasticity inherent in the process itself.

@@

  The obvious rule of thumb derived from the above example is “sample more”, but we note that there are limits to the utility of this motto. Sampling more will clearly reduce uncertainty regarding the upper bound of the probability of interaction, and it will also increase the probability of detecting unlikely interactions (i.e. interactions occurring with a low probability). Yet, since the probability of observing the co-occurrence of two species will always be higher than the probability of observing their interaction (since the probability of interaction is conditional on both interaction partners being present), we will accumulate observations of co-occurrences faster than we will accumulate observations of interactions. Thus, the more we sample, the more zeros will appear in our interaction matrix, which may seem like a counter-intuitive outcome.

@@

@@

  To progressively dissect the different contributions to uncertainty, we will start by considering how we could naively quantify interaction probability and its associated uncertainty \emph{for an interaction that has not yet been observed}. We consider that a pair of species have been observed $n$ times co-occurring at one location, and the number of times they have been observed interacting is $k = 0$. We now aim to evaluate the uncertainty of this interaction. The occurrence of an interaction is a Bernoulli trial. Consequently, the number of success $k$ over $n$ trials will follow a binomial distribution:

@@

  The variance of a Bernoulli experiment is $n\lambda$(1-$\lambda$). It is important to remember that this variance describes the variability of the number of success $k$ for $n$ trials and is not the variance associated with the estimation of $\lambda$.
  Given this variance, it is possible to compute the confidence interval for the MLE of $\lambda$ using any of several methods, including the \emph{Wilson score interval}, the \emph{Clopper-Pearson interval}, and the \emph{Agresti-Coull Interval} (for details, see [\citealp{}]). Finding this estimate is therefore quite straightforward, but it nonetheless has two drawbacks. First, $\lambda$ is not a single point estimate but rather a random variable with a given uncertainty, the distribution of which is unknown. This means that even if $k = 0$ in a given sample, this does not necessarily imply that the two species will never interact. What it implies is that no interaction is the most likely situation but there is nonetheless a significant chance that the two species \emph{could} interact. In contrast with the situation where $k>0$, when we are sure that an interaction is feasible, 
  % (in which case, the ratio $k/n$ is smaller than $n$ because of detection and process uncertainty),  % This parenthetical makes the sentence very long. Is it necessary?
  we are not sure that absence of interactions is caused by $L=0$. Second, and most importantly, the number of trials $n$ might be very low in many instances (and some pairs of species might not have been documented as co-occuring in even one case). Consequently, the uncertainty in the estimation of $\lambda$ might be considerable. In Fig.~\ref{upper_limits}, we derive the Clopper-Pearson interval to explore how the estimate of $\lambda$ varies with sample size. At a small sample size, the 95\% confidence interval spans all values of $\lambda$. To establish that species are not interacting with any acceptable certainty requires tens of observations of the two species co-occurring but not interacting.
  % Is the Clopper-Pearson interval the one in Dom's code snippets? If so, this is Fig.~\ref{Salix_cdfs}

@@

  MLE is zero if no interactions detected, but there may still be a substantial probability of interaction should the two species co-occur. [This is particularly important in the context of a changing world, where species not co-occurring today – or species not detected co-occurring today – may well do so tomorrow, forming complex interactions.]

@@

          In the literature of ecological networks there is a solid collection of data for which know network connectance and from which we can define the connectance distribution. Connectance is measured as $C = L/S^2$, where $L$ is the number of interactions and $S$ is the number of species. It measures the filling of an interaction matrix and thereby expresses the average probability that any two species interact with each other. If we know only the mean $\overline{C}$ and the variance $\sigma_C^2$ of the distribution of $C$, then the beta parameters could be computed as follows using the method of moments:

@@

  %Perhaps we want to also have a trait matching example in addition to the degree distribution example below?
  % Are degree distributions valid priors for interaction probabilities in a unipartite web? For the Salix-gall dataset we're using interaction probabilities as priors (since the degree of both Salix and galler matter)... maybe we should rephrase this to predict the degree of species $i$ based on the degrees of 10 other species in the network?
  The Bayesian framework can be illustrated with a simple quantitative example. Suppose we have $n = 10$ observations of co-occurrence between species $i$ and species $j$ in a given time interval and area, and $X = 3$ observations of interactions. The maximum likelihood estimate of the interaction probability is simply $\theta_{MLE} = 3/10 = 0.3$. 
  % We should probabaly have a value  on the interaction probablitity that differs from the average of the degree distrbution
   Now consider we know that species $i$ is known to interact with 10 other species, which have the following normalised degrees:

@@

    Adding the observed data (n=10, k=3) and using the same code,
    we obtain posterior hyper parameters $\alpha'$=4.05083 and $\beta'$=12.36589 and a posterior mean 0.247 and variance 0.011 for the probability of. Comparing the posterior distribution to the prior, we see that the posterior is closer to the observed data and that the additional data has reduced the variance.

@@

    The exercise exemplified above yields a surprising result: it requires \textgreater24 observations of no interactions to be 95\% sure that the interaction probability is smaller than 0.1 (recall Fig.~\ref{upper_limits}). Note the special case where there is no observation of the two species co-occurring and failing to interact, $n = 0$. In this situation, the posterior distribution converges to the prior distribution since the data include no information on the probability with which species might interact should the co-occur; see above).

@@

    It is fairly straightforward to compute most of network metrics when the different $\lambda$ of the adjacency matrix are known, without variance~\citep{Poisot2016}. Several of these metrics derive directly from quantitative indices of network structure which are equivalent to $\lambda$; the remainder, originally defined for binary networks, can be adjusted to account for interaction probabilities between zero and one. It is not as easy, however, to understand how the uncertainty in these estimated interaction probabilities influences network metrics. Computation of these metrics involves non-linear functions and therefore, because of Jensen's inequality (which states that the average of non-linear function of a stochastic variable differs from the function of the average of that variable), any uncertainty in $\lambda$s could bias both the mean and variance of a network metric. For instance, assume that among all pairs of species with few observed co-occurrence there are many pairs which truly interact.    If we begin with no observed links for these pairs, then correcting for these false absences will inflate the number of links and consequently influence metrics such as connectance, nestedness, and degree distribution. While we can, as described above, calculate these network metrics using fixed estimates for $\lambda$ no analytical solution currently exists for uncertain $\lambda$. Instead we must rely on computer simulations. In the following section, we will provide an empirical example, based on the data set published by~\citet{Kopelke2017}. We will show how the uncertainty arising from both absences of co-occurrences and false absences of interactions impact these metrics. We find uncertainty influences both the average and the variance of network metrics, putting in perspective traditional network comparison studies where these metrics are assumed fixed entities.

@@

      We use an extensively sampled \emph{Salix}-galler-parasitoid meta-network as a case study. This dataset consists of a single community type sampled across Europe, including willow (\emph{Salix}) species, willow-galling sawflies (Hymenoptera, Tenthredinidae, Nematinae, Euurina), and their natural enemies (hymenopteran parasitoids and coleopteran, lepidopteran, dipteran, and hymenopteran inquilines). The data was collected over 29 years (1982-2010) at 374 unique locations across Europe ranging from Sicily to the Arctic. Including repeated visits to a number of sites, the data set contains 641 site-visits, each of which can be considered as a network in its own right. Here we consider each network as an independent sample from which to build the meta-network. The meta-network consists of 1,173 different interactions between 52 \emph{Salix} nodes, 92 herbivore nodes and 126 natural enemy nodes. Interactions were determined by dissecting and rearing gall inhabitants from 165,424 galls. The high spatiotemporal resolution of this network and the unusually high sampling effor implemented at the site level (641 site-visits, which can be considered as repeated samples of the network) makes this dataset particularly well suited for testing this method.

      Importantly, while large, this network will illustrate the very real constraints on the sampling of ecological networks. As a baseline pattern, we may compare the frequency of co-occurrence of taxa in the example data set to the pattern of Fig.~\citep{upper_limits}. In the example data, most (3986 out of 4992) pairs of species are never found co-occurring, and for species found co-occurring the number of co-occurrences was generally low (Fig.~\ref{histograms}A). Among the species which did sometimes interact when co-occurring, the incidence of interaction was actually low. Only 141 pairs of species were observed interacting: of these, 26 were observed interacting only once and 48.2\% were observed interacting five or fewer times (Fig.~\ref{histograms}B). Thus, even in the most extensive data set that we could think of, limited sampling is clearly a major source of uncertainty.

@@

      For species where no co-occurrence were observed, we can 
      calculate the MLE estimates for the mean and variance of 
      $\lambda_{ij}$ directly from this prior following 
      equations~\ref{mean} and~\ref{variance} 
      (see \emph{Appendix S2} for R implementation). The prior 
      distribution we obtain based on~\citet{Barbour2016,Barbour2016Dryad} is:
      $\hat{\lambda_{ij}}$=0.570, var($\lambda$)=0.056 for the \emph{Salix}-galler network and $\hat{\lambda_{ij}}$=0.124, var($\lambda$)=0.010 for the galler-parasitoid network.
      This is consistent with the prior data, where the average 
      interaction probability based on the degree distributions of Salix genotypes and gallers was 0.562 and that for gallers and parasitoids was 0.122. These probabilities are much higher than those in our dataset (0.028 and 0.078 for the \emph{Salix}-galler and galler-parasitoid networks, respectively). This discrepancy may reflect the differences in scale between a network containing different genotypes of a single \emph{Salix} species and four gallers from a single family and a network containing many \emph{Salix} species and gallers from many families as is the case in our dataset.

      For a pair of species where some co-occurrence were observed, we can update the prior distribution with these data. If we consider only pairs of species which were observed to co-occur but not to interact, $k_{ij}$ is always 0 and only $n_{ij}$ will vary between species pairs. Thus $\alpha'$=$\alpha$ and $\beta'$=$\beta + n$. At the most extreme case, for a pair of species which co-occurred at all 374 sites and was never observed to interact, our distributions would become:

@@

      With species $i$ and $j$ co-occurring at all 374 sites and never being observed to interact, the maximum likelihood expectation for the probability of an interaction $ij$ is very close to 0 and the variance about this estimate is very narrow. In other words, we could establish with high certainty that the species will never interact. However, for most pairs of species $i$ and $j$, the species did not co-occur at so many sites and our posterior mean and variance retain some influence of the prior. Nevertheless, as the number of observed co-occurrence increases, the posterior mean becomes closer to zero and the posterior variance decreases (Fig.~\ref{Salix_pdfs}).

@@

      As well as obtaining posterior means and variances, it is possible to calculate a 95\% credible interval about the posterior mean. This is again straightforward to do in R (see the function ``credible interval" in \emph{Appendix S2}). Calculating the 95\% credible intervals for species pairs with 0 to 50 observed co-occurrences without any observed interaction (as in Fig.~\ref{Salix_pdfs}), we see that the interval narrows dramatically as the number of observations increases. In no case, however, does the confidence interval include 0. Even for a pair of species which appeared together in all 374 sites but were never observed interacting, the confidence interval (0.001, 0.018) comes close to, but does not include zero (Table~\ref{interval_table}). In other words, even with a very large data set, we will have problems in establishing that a given species pair can never interact.

@@

    After obtaining these posterior networks, we calculated the connectance of each web, as well as the number of links per resource (\emph{Salix} in the \emph{Salix}-galler networks or galler in the galler-parasitoid networks) and links per consumer. To demonstrate how these network metrics will be affected by detection uncertainty, we then created a suite of filtered networks for each posterior network. Networks were filtered by randomly sampling 99\%, 95\%, 90\%, 80\%, 70\&, 60\%, and 50\% of the interactions included in each posterior network. For level of detection accuracy, we created 100 randomly-sampled network per posterior-probability network. We then calculated the same network properties as described above.

>>>>

    Efforts to account for variance in interaction frequencies are complicated by the fact that not only interaction frequencies but also network structure vary over space and time. Community composition and species abundances vary from site to site~\citep{Baiser2012} and over time within a site~\citep{Olesen2011a}. The removal of a species from a site will obviously also remove its interactions. Interactions can also be lost, however, if participating species remain present but do not co-occur temporally or are too rare to detect each other~\citep{Tylianakis2010}, or through changes to individual preferences~\citep{Fodrie2015}.

    Beyond "true" variation in network structure, several researchers have pointed to the importance of sampling intensity for the assessment of network structure (e.g.,~\citealp{Martinez1999,Bluthgen2006,XX}). Despite this, the acknowledgment that insufficient sampling effort limits our ability to describe variation in ecological networks has not yet led to a quantitative framework to deal with the uncertainty generated by spatiotemporal variation in ecological interactions and by sampling.

@@

  To define the problem associated with describing ecological interaction networks, we will start from the perspective of an empirical community ecologist faced with the task of describing an interaction network. This ecologist will be interested in generating a description of the blocks present, and the links between them (Roslin and Majaneva 2017). In other words, he or she seeks to fill in a matrix of species by species interactions. Importantly, the information sought is as much [in] the presence of given links as [in] the absence of others. An observed link will always remain an observed link, but as to why given links are not observed, there may be multiple contributions. Thus, we will set off by contemplating what factors may contribute to links missing from the matrix. We consider that there are three nested levels of uncertainty making the occurrence of any interaction a stochastic process:

@@

    First, and most fundamentally, we do not know whether or not a pair of species have the appropriate characteristics to interact. We define the probability of an interaction $L$ as $P(L)=\lambda$. Obviously, because $k=0$ [[k hasn't been defined up to this point]], it is very likely that they cannot interact even if there were no time or environmental constraints preventing the interaction. [[The previous sentence doesn't follow, k hasn't been defined and we don't know that it's zero. Also, are we assuming that these interactions have been observed over a large area/time like the Kopelke data? Otherwise couldn't something about that particular site prevent species interacting even if they otherwise could?]] But it is nonetheless possible that the interaction is a rare phenomenon that has never been documented before. This source of uncertainty is the one documented by trait-matching models~\citep{}. It arises because every model is imperfect and lacks information (i.e. traits) about the constraints on the interaction. In other words, with sufficient sampling and all information accessible, this interaction probability should either tend to 0 or to 1 and the uncertainty vanishes. [[For species which actually co occur (?)]]

@@

    It could be that the interaction is feasible, i.e. $L=1$, but that it does not occur at a given location or moment in time because there are local constraints [[such as...]] preventing it from occurring. We define the realisation of the interaction process $X$, given that the interaction is feasible, as a stochastic process with associated probability $P(X|L)=\chi$. This phenomenon of interaction contingencies is usually not considered in network studies, but there is a rich literature in community ecology about the contingencies of interactions~\citep{}. 
    % We imagine for instance that an interaction between a gall and a parasitoid might not be recorded at a location because it was the wrong time of the year and the gall had not yet formed (phenological constraints), a late frost killed the larvae (an abiotic environmental constraint), another parasitoid species competitively excluded the parasitoid species of interest (a biotic environmental constraint) or simply the parasitoid is too rare to interact with all of its viable hosts (an abundance constraint).

@@

    Lastly, measurement errors are always a source of uncertainty in the observation of ecological processes. We define the detection of an interaction $D$, given an interaction is feasible and occurs in the local conditions, as a stochastic process with associated probability $P(D|X,L)=\delta$. Detection failure could happen for several reasons, for instance if the rearing of a parasitoid fails with inappropriate lab conditions or because of species mis-identification [[or because the interaction is rare enough that we just miss it? Or we're just looking in the wrong place at the wrong time?]]. Some sources of detection error could be minimised with appropriate sampling effort ($\delta$ will converge to one with increasing number of collected galls), but other sources are often difficult to reduce (e.g. the occurrence of cryptic species might require molecular analysis for appropriate taxonomic identification).

@@

    The combination of these three sources of uncertainty together leads to many potential explanations for the observation of an absence of interaction, but only the situation where $L = 0$ (a true absence) is relevant for the investigation of networks. While the observation of an interaction is straightforward to interpret, absence of interactions must be decomposed into different quantities. It is particularly important to rule out the situations where $D=0 \cup X = 1 \cup L=1$, i.e. the interaction occurred at the location but was not observed, and $D=1 \cup X = 0 \cup L =1$, the interaction is feasible and would have been detected but did not occur at the local site.

  It is important to keep in mind that for network analysis, ecologists seek to measure the occurrence of true absences, which is the joint event $L=0 \cup X=1 \cup D=1$), but in reality they measure the marginal probability $P(L) = k/n$. [[k and n still haven't been defined]]% I'm pretty sure this should be L=0 but X=1 and D=1: interaction not feasible but site and detection perfect.

@@

  For the ecologist working on collecting network data, and on later interpreting these data, the considerations above raise a major challenge: how may we infer whether unobserved interactions went undetected due to sampling, or whether they truly do not occur. How then may we refine our sampling approaches to reduce uncertainties, and to gain insights into the impact of multiple processes on field observations? Importantly, some sources [[of uncertainty]] can be minimised with appropriate sampling design and efforts, while other sources are difficult or impossible to reduce – since they are generated by chance variation created by the very process in which we are interested.

  The basic information that we are collecting consists of matrices of interaction partners. Our count of interactions between species A and species B reflects uncertainty with respect to whether two species interact when co-occurring at a given site, chance variation in whether the interaction is realised, [[the previous two things sound like the same thing. Maybe ``whether two species are capable of interacting when co-occuring at a given site, chance variation as to whether the interaction is realized...'']] and uncertainty with respect to whether it is detected when realised. In this case, what can we do to pin down any of these different types of variation?

  A simple example will illustrate the problem: assume that we want to infer the probability of an interaction between two species, A and B. Now assume that in reality, interaction between A and B is completely impossible (i.e. the true $\lambda$= 0). Given no added detection error in observing the incidence of the interaction, then a single observation of species co-occurrence will reveal (very) little regarding the probability of the interaction – the confidence limits for one observation essentially spans from 0 to 1 (Fig.~\ref{upper_limits}). For 5 observations, this confidence limit still extends to 0.5. Only with thirty observations will it shrink to 0.1. Thus, adding (many) more observations is certainly useful in controlling uncertainty due to stochasticity inherent in the process itself.

@@

  The obvious rule of thumb derived from the above example is “sample more”, but we note that there are limits to the utility of this motto. Sampling more will clearly reduce uncertainty regarding the upper bound of the probability of interaction, and it will also increase the probability of detecting unlikely interactions (i.e. interactions occurring with a low probability). Yet, since the probability of observing the co-occurrence of two species will always be higher than the probability of observing their interaction (since the probability of interaction is conditional on both interaction partners being present), we will accumulate observations of co-occurrences faster than we will accumulate observations of interactions. Thus, the more we sample, the more zeros will appear in our interaction matrix, which may seem like a counter-intuitive outcome. [[Furthermore, depending on the spatial and temporal extent of our sampling, more sampling may not help us detect feasible interactions which are prevented from being realized by local processes at the sites/times we are sampling.]]

@@

  [[How do we define samples? For the Kopelke set we use sampling occasion, but what about sampling twice as many trees on the same day and same place? Does that count? Does it have to be spatially and/or temporally separated? Is it relevant??]]

@@

  To progressively dissect the different contributions to uncertainty, we will start by considering how we could naively quantify interaction probability and its associated uncertainty \emph{for an interaction that has not yet been observed}. We consider that a pair of species have been observed $n$ times co-occurring at one location, and the number of times they have been observed interacting is $k = 0$. We now aim to evaluate the uncertainty of this interaction. The occurrence of an interaction is a Bernoulli trial. Consequently, the number of success[es] $k$ over $n$ trials will follow a binomial distribution:

@@

  The variance of a Bernoulli experiment is $n\lambda$(1-$\lambda$). It is important to remember that this variance describes the variability of the number of success[es] $k$ for $n$ trials and is not the variance associated with the estimation of $\lambda$.
  Given this variance, it is possible to compute the confidence interval for the MLE of $\lambda$ using any of several methods, including the \emph{Wilson score interval}, the \emph{Clopper-Pearson interval}, and the \emph{Agresti-Coull Interval} (for details, see [\citealp{}]). Finding this estimate is therefore quite straightforward, but it nonetheless has two drawbacks. First, $\lambda$ is not a single point estimate but rather a random variable with a given uncertainty, the distribution of which is unknown. This means that even if $k = 0$ in a given sample, this does not necessarily imply that the two species will never interact. What it implies is that no interaction is the most likely situation but there is nonetheless a significant chance that the two species \emph{could} interact. In contrast with the situation where $k>0$, when we are sure that an interaction is feasible, 
  % (in which case, the ratio $k/n$ is smaller than $n$ because of detection and process uncertainty),  % This parenthetical makes the sentence very long. Is it necessary?
  we are not sure that absence of interactions is caused by $L=0$. Second, and most importantly, the number of trials $n$ might be very low in many instances (and some pairs of species might not have been documented as co-occuring in even one case). Consequently, the uncertainty in the estimation of $\lambda$ might be considerable. In Fig.~\ref{upper_limits}, we derive the Clopper-Pearson interval to explore how the estimate of $\lambda$ varies with sample size. At a small sample size, the 95\% confidence interval spans all values of $\lambda$. To establish that species are not interacting with any acceptable certainty requires tens of observations of the two species co-occurring but not interacting.
  % Is the Clopper-Pearson interval the one in Dom's code snippets? If so, this is Fig.~\ref{Salix_cdfs}

@@

  MLE is zero if no interaction is detected, but there may still be a substantial probability of interaction should the two species co-occur. [This is particularly important in the context of a changing world, where species not co-occurring today – or species not detected co-occurring today – may well do so tomorrow, forming complex interactions.]

@@

          In the literature of ecological networks there is a solid collection of data for which we know network connectance and from which we can define the connectance distribution. Connectance is measured as $C = L/S^2$, where $L$ is the number of interactions and $S$ is the number of species. It measures the filling of an interaction matrix and thereby expresses the average probability that any two species interact with each other. If we know only the mean $\overline{C}$ and the variance $\sigma_C^2$ of the distribution of $C$,[[from the literature or from our network?]] then the beta parameters could be computed as follows using the method of moments:

@@

  %Perhaps we want to also have a trait matching example in addition to the degree distribution example below?
  % Are degree distributions valid priors for interaction probabilities in a unipartite web? For the Salix-gall dataset we're using interaction probabilities as priors (since the degree of both Salix and galler matter)... maybe we should rephrase this to predict the degree of species $i$ based on the degrees of 10 other species in the network?
  The Bayesian framework can be illustrated with a simple quantitative example. Suppose we have $n = 10$ observations of co-occurrence between species $i$ and species $j$ in a given time interval and area, and $X = 3$[ = k?] observations of interactions. The maximum likelihood estimate of the interaction probability is simply $\theta_{MLE} = 3/10 = 0.3$. 
  % We should probabaly have a value  on the interaction probablitity that differs from the average of the degree distrbution
   Now consider we know that species $i$ is known to interact with 10 other species, which have the following normalised degrees:

@@

    Adding the observed data (n=10, k=3) and using the same code,
    we obtain posterior hyper parameters $\alpha'$=4.05083 and $\beta'$=12.36589 and a posterior mean 0.247 and variance 0.011 for the probability of [[...?]]. Comparing the posterior distribution to the prior, we see that the posterior is closer to the observed data and that the additional data has reduced the variance.

@@

    The exercise exemplified above yields a surprising result: it requires \textgreater24 observations of no interactions to be 95\% sure that the interaction probability is smaller than 0.1 (recall Fig.~\ref{upper_limits}). Note the special case where there is no observation of the two species co-occurring and failing to interact, $n = 0$ [[shouldn't it just be ``no observation of the two species co-occuring, $n=0$.'' I.e. nothing about failing to interact? Wouldn't that be $n = k$ and then you're pretty certain that an interaction does indeed exist?]] In this situation, the posterior distribution converges to the prior distribution since the data include no information on the probability with which species might interact should they co-occur; see above).

@@

    It is fairly straightforward to compute most of network metrics when the different $\lambda$ of the adjacency matrix are known, without variance~\citep{Poisot2016}. Several of these metrics derive directly from quantitative indices of network structure which are equivalent to $\lambda$; the remainder, originally defined for binary networks, can be adjusted to account for interaction probabilities between zero and one. It is not as easy, however, to understand how the uncertainty in these estimated interaction probabilities influences network metrics. Computation of these metrics involves non-linear functions and therefore, because of Jensen's inequality (which states that the average of non-linear function of a stochastic variable differs from the function of the average of that variable), any uncertainty in $\lambda$s could bias both the mean and variance of a network metric. For instance, assume that among all pairs of species with few observed co-occurrences there are many pairs which truly interact.    If we begin with no observed links for these pairs, then correcting for these false absences will inflate the number of links and consequently influence metrics such as connectance, nestedness, and degree distribution. While we can, as described above, calculate these network metrics using fixed estimates for $\lambda$ no analytical solution currently exists for uncertain $\lambda$. Instead we must rely on computer simulations. In the following section, we will provide an empirical example, based on the data set published by~\citet{Kopelke2017}. We will show how the uncertainty arising from both absences of co-occurrences and false absences of interactions impact these metrics. We find uncertainty influences both the average and the variance of network metrics, putting in perspective traditional network comparison studies where these metrics are assumed [[to be]] fixed entities.

@@

      We use an extensively sampled \emph{Salix}-galler-parasitoid meta-network as a case study. This dataset consists of a single community type sampled across Europe; willow (\emph{Salix}) species, willow-galling sawflies (Hymenoptera, Tenthredinidae, Nematinae, Euurina), and their natural enemies (hymenopteran parasitoids and coleopteran, lepidopteran, dipteran, and hymenopteran inquilines). The data were collected over 29 years (1982-2010) at 374 unique locations across Europe ranging from Sicily to the Arctic. Including repeated visits to a number of sites, the data set contains 641 site-visits, each of which can be considered as a network in its own right. Here we consider each network as an independent sample from which to build the meta-network. The meta-network consists of 1,173 different interactions between 52 \emph{Salix} nodes, 92 herbivore nodes and 126 natural enemy nodes. Interactions were determined by dissecting and rearing gall inhabitants from 165,424 galls. The high spatiotemporal resolution of this network and the unusually high sampling effor implemented at the site level (641 site-visits, which can be considered as repeated samples of the network) makes this dataset particularly well suited for testing this method.

      Importantly, while large, this network will illustrate the very real constraints on the sampling of ecological networks. As a baseline pattern, we may compare the frequency of co-occurrence of taxa in the example data set to the pattern of Fig.~\citep{upper_limits}. In the example data, most (3986 out of 4992) pairs of species are never found co-occurring, and for species found co-occurring the number of co-occurrences was generally low (Fig.~\ref{histograms}A). Among the species which did sometimes interact when co-occurring, the incidence of interaction was actually low. Only 141 pairs of species were observed interacting: of these, 26 were observed interacting only once and 48.2\% were observed interacting five or fewer times (Fig.~\ref{histograms}B). Thus, even in the most extensive data set that we could find, limited sampling is clearly a major source of uncertainty.

@@

      For species where no co-occurrences were observed, we can 
      calculate the MLE estimates for the mean and variance of 
      $\lambda_{ij}$ directly from this prior following 
      equations~\ref{mean} and~\ref{variance} 
      (see \emph{Appendix S2} for R implementation). The prior 
      distribution we obtain based on~\citet{Barbour2016,Barbour2016Dryad} is:
      $\hat{\lambda_{ij}}$=0.570, var($\lambda$)=0.056 for the \emph{Salix}-galler network and $\hat{\lambda_{ij}}$=0.124, var($\lambda$)=0.010 for the galler-parasitoid network.
      This is consistent with the prior data, where the average 
      interaction probability based on the degree distributions of Salix genotypes and gallers was 0.562 and that for gallers and parasitoids was 0.122. These probabilities are much higher than those in our dataset (0.028 and 0.078 for the \emph{Salix}-galler and galler-parasitoid networks, respectively). This discrepancy may reflect the differences in scale between a network containing different genotypes of a single \emph{Salix} species and four gallers from a single family and a network containing many \emph{Salix} species and gallers from many families as is the case in our dataset.

      For a pair of species where some co-occurrences were observed, we can update the prior distribution with these data. If we consider only pairs of species which were observed to co-occur but not to interact, $k_{ij}$ is always 0 and only $n_{ij}$ will vary between species pairs. Thus $\alpha'$=$\alpha$ and $\beta'$=$\beta + n$. At the most extreme case, for a pair of species which co-occurred at all 374 sites and was never observed to interact, our distributions would become:

@@

      With species $i$ and $j$ co-occurring at all 374 sites and never being observed to interact, the maximum likelihood expectation for the probability of an interaction $ij$ is very close to 0 and the variance about this estimate is very narrow. In other words, we could establish with high certainty that the species will never interact. However, for most [[all??]] pairs of species $i$ and $j$, the species did not co-occur at so many sites and our posterior mean and variance retain some influence of the prior. Nevertheless, as the number of observed co-occurrence increases, the posterior mean becomes closer to zero and the posterior variance decreases (Fig.~\ref{Salix_pdfs}).

@@

      As well as obtaining posterior means and variances, it is possible to calculate a 95\% credible interval about the posterior mean. This is again straightforward to do in R (see the function ``credible interval" in \emph{Appendix S2}). Calculating the 95\% credible intervals for species pairs with 0 to 50 observed co-occurrences without any observed interaction [[ were there any species with 50 co-occurrences and no interaction?]] (as in Fig.~\ref{Salix_pdfs}), we see that the interval narrows dramatically as the number of observations increases. In no case, however, does the confidence interval include 0. Even for a pair of species which appeared together in all 374 sites but were never observed interacting, the confidence interval (0.001, 0.018) comes close to, but does not include zero (Table~\ref{interval_table}). In other words, even with a very large data set, we will have problems in establishing that a given species pair can never interact.

@@

    After obtaining these posterior networks, we calculated the connectance of each web, as well as the number of links per resource (\emph{Salix} in the \emph{Salix}-galler networks or galler in the galler-parasitoid networks) and links per consumer. To demonstrate how these network metrics will be affected by detection uncertainty, we then created a suite of filtered networks for each posterior network. Networks were filtered by randomly sampling 99\%, 95\%, 90\%, 80\%, 70\&, 60\%, and 50\% of the interactions included in each posterior network. For each level of detection accuracy, we created 100 randomly-sampled networks per posterior-probability network. We then calculated the same network properties as described above.

    Note that the posterior webs for the Salix-galler network all had much higher connectance than the original, observed web (C=0.028 for the observed web, Fig.~\ref{posterior_webs}). Likewise, the number of links per \emph{Salix} and galler species in the observed web (2.71 and 1.47, respectively) were much lower than those predicted in the posterior webs, even when filtering with a detection probability of only 50\%. There are two possible explanations for this discrepancy: either the~\citet{Barbour2016} data do not give an appropriate prior for our dataset, or the true detection probability for links between \emph{Salix} and galler species is much less than 50\%. As the scale of the two datasets is quite different (genotypes of a single \emph{Salix} species in~\citet{Barbour2016}, various \emph{Salix} species in our dataset), we suspect the former is more likely.
